Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-17 thesis/acknowledgments.tex
finalizing

\vspace{0.8cm}
% Thank people, places, things, existential concepts, etc. here. Length varies
% but usually something like 1-2 pages

To my wife Ellen, who moved across the country for me to NYC and will be moving
across the country again in the next few months, who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but its a good thing
I have the rest of my life to show how grateful I am.

To my parents and my family who have continued to support me in countless ways
throughout my life. \textbf{...more...}

>>>>

\vspace{0.8cm}

To my wife Ellen, who moved across the country for me to NYC
(and across the country again in the next few months), who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but its a good thing
I have the rest of my life to show how grateful I am.

To my family who have continued to support me in countless ways.
In many ways my parents are directly responsible for me pursuing a career in Astronomy.
They enabled me to have a good education throughout my life that prepared me
well for graduate school. But maybe more importantly, they provided me with my
first exposure to the wonders of the Universe which gave me the desire to
pursue the path that led me to where I am today.
